\chapter{Technical Work}

\section{Technical Considerations,Requirements ??}
\subsection{Cell Selection}
What is the ideal cell to use, price, quality, specific energy charge recharge efficiency, safety
\subsection{Physical Considerations}
Battery Box shape material design, ergonomics.
Module design, how the cells connect together to form a module electrically and mechanically.
Intermodule connection, reliable has to resist 3000km + of highway vibration
Pack layout module placement securing, fuse breaker placement, interconnects
\subsection{Electrical Considerations}
What is the best series parallel combination to give the ideal battery, voltage etc, fuse breaker, connectors
Bus voltage considerations, max lower speed, max top speed, better acceleration. Tracker and motor controller efficiencies.
\subsection{Battery Monitoring System}
Why monitoring is important, what needs to be monitored. 


\section{Design}
\subsection{Physical Design}
\subsubsection{Module Design}
\subsubsection{Interconnect Design}
\subsubsection{Battery Box}
\subsubsection{Layout}


\subsection{Electrical Design}
calculated ideal bus voltage
\subsection{Battery Monitoring System}
bms desing and development
\subsubsection{Hardware Design}
part selection, pcb desing considerations, manufacturing process
\subsubsection{Firmware Design}


\section{Testing, Results}
\subsection{Physical Considerations}
\subsection{Electrical Considerations}
\subsection{Battery Monitoring System}
\subsection{Discharge/Charge Testing}
Test the integrity of cells and modules within the pack, all cleared out, test for out of balance cells.
Discharge the pack at known constant currents to determine the internal impedance, and the characteristic voltage of the battery pack, useful for state of charge estimation.
Second order characterisations

\section{Further Work and possible improvements}
Further pack characterisation, further development of physical design and battery box. BMS improvements, simpler cheaper BMS? Machined laser cut parts for bms interconnects and battery box. 

